Analysis of H-1B Visa Workers Using H-1B LCA Disclosure Data (2020–2024)

### 2025-01-31 products/manuscript/Manuscript.qmd
data clean

The raw data import and cleaning will be conducted seprately since the dataset is large.

>>>>

```{r}
# load packages
library(here)
library(dplyr)

# load raw data
LCAraw <- read.csv(here("data", "raw-data", "LCA2020to2024.csv"))

# get the overview of the data
dim(LCAraw)
head(LCAraw)

# clean the data
LCAdata <- LCAraw %>%
  filter(CASE_STATUS == "Certified", VISA_CLASS == "H-1B") %>%
  select(RECEIVED_DATE, SOC_TITLE, EMPLOYER_NAME, EMPLOYER_STATE, WORKSITE_STATE, WAGE_RATE_OF_PAY_FROM, PREVAILING_WAGE)

# take a look at the processed data
head(LCAdata)

# save as rds
save_data_location <- here::here("data","processed-data","LCAdata.rds")
saveRDS(LCAdata, file = save_data_location)

```
